\documentclass{article}
  % Packages
  \usepackage{fontspec}
    \setmainfont{Charis SIL}
  \usepackage{hyperref}
    \hypersetup{colorlinks=true, allcolors=blue}

  % Commands
  \newcommand{\tabhead}[1]{\textbf{#1}}

  % Document info
  \title{\textsc{
           University of Georgia \\
           Consent Form \\
         }
         The expression of race in Louisiana French among Creoles and Cajuns}
  \date{}

  \begin{document}
    \maketitle
    You are being asked to take part in a research study.
    The information in this form will help you decide if you want to be in the study.
    Please ask the researcher below if there is anything that is not clear or if you need more information.
    \begin{center}
      \begin{tabular}{l l}
        \tabhead{Principal Investigator:}                  & \tabhead{Co-Investigator:} \\
        Jon Forrest                                        & Joshua McNeill \\
        University of Georgia                              & University of Georgia \\
        Linguistics Department                             & Linguistics Department \\
        706-542-5099                                       & 504-264-2474 \\
        \href{mailto:jrforrest@uga.edu}{jrforrest@uga.edu} & \href{mailto:joshua.mcneill@uga.edu}{joshua.mcneill@uga.edu}
      \end{tabular}
    \end{center}

    \section{Purpose of study}
      The researcher is doing this research to learn more about race and ethnicity in Louisiana and what role, if any, race and ethnicity play in the way people speak French and Creole in Louisiana.
      In order to make this study a valid one, you will not be made fully aware of nor be misled about the nature or purpose of the study.

    \section{Eligibility}
      You are being invited to take part in this study because you speak French or Creole and self-identify as a Creole or a Cajun.

    \section{What you are being asked to do}
      If you agree to take part in this study, you will:
      \begin{enumerate}
        \item Complete an audio recorder interview with the researcher about your background, experiences, and views on race and ethnicity. (45-60 minutes)
        \item Complete a survey that involves naming people in your social network and several details about each of them. (10-15 minutes)
        \item Complete a translation task that involves translating English sentences into French or Creole. (10-15 minutes)
      \end{enumerate}
      You are therefore being asked to spend between 1 hour 5 minutes to 1 hour 30 minutes with the researcher.

    \section{Participation is voluntary}
      You can refuse to take part or stop at any time without penalty.

    \section{Potential risks}
       \begin{itemize}
         \item You may feel uncomfortable providing your voice to the researcher.
         \item You may feel uncomfortable discussing race, ethnicity, or other subjects that come up during the interview.
       \end{itemize}

    \section{Potential benefits}
      \begin{itemize}
        \item You may feel satisfaction from lending your voice to research on your language and people.
        \item You may be interested in discussing these topics with the researcher.
      \end{itemize}

    \section{Confidentiality}
      The researcher will take steps to protect your privacy.
      The audio recording and transcript of your interview will be stored on a secure server on a private internet storage site. However, there is always a small risk that your information could be accidentally disclosed to people not connected to the research.
      To reduce this risk:
      \begin{itemize}
        \item Names will be removed from the audio recording.
        \item Names will be anonymized in the transcript of the audio recording.
      \end{itemize}
      Be aware that your audio recording and transcript may be shared with other researchers for future studies.
      In these cases, only the censored and anonymized versions will be shared.

    \section{Consent}
      By signing below, I, \rule{3cm}{0.4pt}, acknowledge the following:
      \begin{itemize}
        \item A copy of the procedures of this investigation and a description of any risks, discomforts and benefits associated with my participation has been provided and discussed in detail with me.
        \item I understand that I have the option to decline to answer any interview or survey questions.
        \item I understand that I can pause the audio recording at any time.
        \item I understand that my participation in this research project is voluntary.
      \end{itemize}

      \noindent\begin{tabular}{l l l}
                                       &                              & \\
                                       &                              & \\
        \rule{0.35\textwidth}{0.4pt}   & \rule{0.35\textwidth}{0.4pt} & \rule{0.2\textwidth}{0.4pt} \\
        Name of researcher             & Signature                    & Date \\
                                       &                              & \\
                                       &                              & \\
        \rule{0.35\textwidth}{0.4pt}   & \rule{0.35\textwidth}{0.4pt} & \rule{0.2\textwidth}{0.4pt} \\
        Name of participant            & Signature                    & Date \\
      \end{tabular}

    \section{Follow-up}
      Please feel free to ask questions about this research at any time.
      You can contact the co-investigator, Joshua McNeill, at 504-264-2474, \href{mailto:joshua.mcneill@uga.edu}{joshua.mcneill@uga.edu} or the principal investigator, Jon Forrest, at 706-542-5099, \href{mailto:jrforrest@uga.edu}{jrforrest@uga.edu}.
      If you have any complaints or questions about your rights as a research volunteer, contact the IRB at 706-542-3199 or by email at \href{mailto:IRB@uga.edu}{IRB@uga.edu}.
  \end{document}
